They are Very Smart: Genetic-Algorithm-Based Pathfinding in Games

### 2018-12-10 paper.tex
More work on paper

>>>>

\imfig{ZombieAgentVision}{The methods for keeping track of GameObjects entering
  and exiting a Zombunny's visionCollider}

Figure 15 shows the OnTriggerEnter and OnTriggerExit methods of the ZombieAgent
class, which are used in conjunction with a Zombunny's visionCollider to update
the inVision HashSet whenever a GameObject enters or exits the Zombunny's
visionCollider radius.

\imfig{ZombieAgentUpdateNearby}{The portions of the FixedUpdate method for
determining the position of nearby objects relative to a Zombunny}

Figure 16 shows the functions used to determine the position of GameObjects in
inVision relative to a Zombunny's previous direction vector, stored as a
dictionary of Targetables to PolarVectors. This allows a Zombunny to keep track
of visible GameObjects relative to where it is currently facing.

\imfig{ZombieAgentUpdateMovement}{The function of FixedUpdate for handling
  movement between ticks}

Figure 17 shows the portion of FixedUpdate dedicated to rotating a Zombunny from
tick to tick, calling the Rotate method of the lastVelocity PolarVector using
the CalculateDirection method of the genome class, taking into account the
Zombunny's previous velocity vector, the time alive, the Zombunny's current
health, and the aforementioned dictionary of nearby GameObjects.

\imfig{ZombieAgentUpdateDeath}{The portion of FixedUpdate that handles
  death/deletion}

Figure 18 shows the part of the FixedUpdate method which keeps track of Zombunny
death, destroying the Zombunny GameObject at the appropriate time and calling
the relevant death animations. For every tick that a Zombunny is not dead,
FixedUpdate will increment timeAlive, which is later used as a factor in
calculating fitness.

\subsubsection{ZombieAttacker}

The ZombieAttacker class calls Update on each tick, dealing damage to any item
in toAttack, which is a HashSet of Targetable GameObjects that intersect with
a Zombunny's attack collider (see Figure 4). This way, a Zombunny can attack
multiple GameObjects so long as they intersect with its attack collider. Damage
is applied to items in toAttack by calling their individual takeDamage methods,
with the damage dealt as determined by the Zombunny's genome passed as a
parameter.

\imfig{}{}
